\label{sec:4.5}

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%(GAO) Discuss ColdADC Power Consumptions
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

The ColdADC is designed with serval power rails with 3 different voltages: VDDA2P5/VDDD2P5 = 2.25 V, VDDIO = 2.25 V, 
and VDDD1P2 = 1.1 V. To achieve good ADC performance, the voltages are elevated to account for IR drop and other
design issues. The  VDDA2P5/VDDD2P5 voltage is raised to 2.5 V when using CMOS reference (2.7 V when using BGR), and 
VDDD1P2 to 2.1 V.
Table~\ref{tab:powerconsumed} shows the measured power consumption under several operating configuration. If ColdADC is powered as 
the design expected, the power consumption is $\approx$ 20 mW per channel with SDC  bypassed (powered down).  If SDC is enabled, 
each channel will consume an extra $\approx$ 6 mW.  When BGR reference is applied, with the elevated VDDA2P5/VDDD2P5 at 2.7 V, the measured
power consumption is $\approx$ 30 mW per channel with SDC powered down.  If CMOS reference is applied, VDDA2P5/VDDD2P5 can be set to 
2.5 V to mitigate the power consumption, which is $\approx$ 26 mW per channel. The issue of raising VDDA2P5/VDDD2P5 to 2.7 V is 
related to the instantiation of an OTA with the wrong input pair polarity (to be discussed in Section~\ref{sec:5.8}).  VDDD1P2 must 
be raised to 2.1 V due to the lack of DC voltage level shifters between 1.2 V and 2.5 V domains (to be discussed in Section~\ref{sec:5.2}). 
Both issues will be addressed in the next version of the ColdADC. We expect power consumption using 
BGR or CMOS references will be roughly the same, and the overall power consumption will be lowered with the new chip.
\begin{table}[h]
\centering
\begin{tabular}{|c|c|c|c|c|c|c|}
\hline
%\textbf{ Temperature  } & \textbf{Value} & \textbf{Result} & \textbf{Note}  \\ \hline \hline
\textbf{Temperature} & RT & RT & RT & LN$_2$ & LN$_2$ & LN$_2$ \\ \hline
\textbf{Reference} & BGR & BGR & CMOS & BGR & BGR & CMOS \\ \hline
\textbf{SDC} & enable & bypassed & bypassed & enable & bypassed & bypassed \\ \hline
\textbf{VDDA2P5/VDDD2P5/ V} & 2.5 &2.5 &2.5 &2.5 &2.5 &2.5 \\ \hline
\textbf{VDD1P2 / V} & 2.1 & 2.1 & 2.1 & 2.1 & 2.1 & 2.1 \\ \hline
\textbf{VDDIO / V} & 2.25 & 2.25 & 2.25 & 2.25 & 2.25 & 2.25  \\ \hline
\textbf{Total Power / mW} & 515 & 418 & 418 & 563 & 513 & 425 \\ \hline
\textbf{Power per Channel / mW} & 32.2 & 26.1 & 26.1 & 35.2 & 32.1 & 26.6 \\ \hline
\end{tabular}
\caption{Power Consumption for ColdADC Chip\#00067}
\label{tab:powerconsumed}
\end{table}  

